Mysterious radio flashes to be used to trace Universe's largest structures

### 2015-08-05 writeup/summary.tex
Added justification text.

>>>>

%%%%% Justification text for submission. %%%%
The study of the large-scale structure of the Universe has the potential to
shed light on aspects of fundamental physics including the nature of
cosmological inflation, the nature of dark energy, and the properties of
neutrinos.  It is thus of broad appeal to the physics community. This work
opens up a new way to study large-scale structure in three dimensions and is
observationally relevant on short time scales of the next few years.
